Morgue: Supplementary material

### 2018-09-21 temporary_morgue/morgue_supp_mat.Rmd
getting organized

>>>>

```{r Interval plots of univariate landscapes}
## Interval Plot: Relative Fitness ----   
bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
  #group_by(Food_Web) %>%
  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
  ggplot(., aes(x=sc.gall_size, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)

## Interval Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)

## Interval Plot: Relative Fitness ----

bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
  group_by(Food_Web) %>%
  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
  ggplot(., aes(x=sc.clutch_size, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)

## Interval Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.clutch_size, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)

## Interval Plot: Relative Fitness ----

# unclear to me why the complex intervals are weird...
bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
  #group_by(Food_Web) %>%
  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
  ggplot(., aes(x=sc.female_preference, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)

## Interval Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.female_preference, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
```

```{r OLD Gall Size Fitness Landscape, eval=FALSE}

## Control ----
RF_control_gall_size <- bootstrap_fitness(
  logistic_model = glmer_control, 
  newdata = expand.grid(
     sc.gall_size = seq(-2,2,length.out=1000), #sort(control_df$sc.gall_size),
     sc.clutch_size = 0,
     sc.female_preference = 0),
  bootstraps=100)

## Treatment ----
RF_treatment_gall_size <- bootstrap_fitness(
  logistic_model = glmer_treatment, 
  newdata = expand.grid(
     sc.gall_size = seq(-2,2,length.out=1000), #sort(treatment_df$sc.gall_size), 
     sc.clutch_size = 0,
     sc.female_preference = 0),
  bootstraps=100)

## Spaghetti Plot: Relative Fitness ----   
bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
  select(-sc.clutch_size, -sc.female_preference) %>%
  gather(ID, fitness, -sc.gall_size, -Food_Web) %>%
  group_by(ID, Food_Web) %>%
  mutate(relative_fitness = fitness/mean(fitness)) %>%
  ungroup() %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.gall_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

## Interval Plot: Relative Fitness ----   
bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
  group_by(Food_Web) %>%
  mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
  ggplot(., aes(x=sc.gall_size, y=relative_fitness)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower_RF, ymax=upper_RF, fill=Food_Web), alpha=0.25)

## Spaghetti Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
  select(-sc.clutch_size, -sc.female_preference) %>%
  gather(ID, fitness, -sc.gall_size, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.gall_size, y=fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.1)) +
  scale_size_manual(values=c(1.5,0.25))

## Interval Plot: Absolute Fitness ----   
bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=average)) +
  geom_line(aes(color=Food_Web)) +
  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
```
